A Logistic Regression Qpproach to CoIL Challenge 2000

### 2019-11-08 final project/Manuscript.Rmd
Updated Final Project

---
title             : "Fall 2019 DATA 621 Final Project"
shorttitle        : "Arnouts et al. Final Project"
author: 
  - name          : "Corey Arnouts"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "119 W 31st St., New York, NY 10001"
    email         : "Corey.Arnouts@spsmail.cuny.edu"
  - name          : "Adam Douglas"
    affiliation   : "1"
  - name          : "Jason Givens-Doyle"
    affiliation   : "1"
  - name          : "Michael Silva"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "CUNY School of Professional Studies"
authornote: |
  MS in Data Science Students
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

@@

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "CoIL Challenge, Logistic Regression"
wordcount         : "X"
bibliography      : ["Manuscript.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf:
    citation_package: biblatex
  html_document: default
---

@@

# Introduction
```{r eval=FALSE, echo=FALSE}
#Describe the background and motivation of your problem.
```
Busineses use data science to extract insight from data.  It has many practical business applications.  The CoIL Challenge showcases the power data science can bring to bear on fundamental business problems.

The CoIL Challenge was a datamining competition organized by the the Computational Intelligence and Learning Cluster. It was held in the period of March-May 2000.  The COIL Challenge had two tasks:

- Predict which customers are potentially interested in a caravan insurance policy; and
- Describe the actual or potential customers; and possibly explain why these customers buy a caravan policy.

In total 43 solutions were submitted. The winners of the challenge were Charles Elkan for the prediction task and Nick Street and YongSeog Kim for the description task.

In this paper we set out to complete the COIL Challenge ourselves using a logistic regression classifier. **SUMARISE FINDINGS**

@@

Discuss how other researchers have addressed similar problems, what their achievements are, and what the advantage and drawbacks of each reviewed approach are. Explain how your investigation is similar or different to the state-of-theart. Please cite the relevant papers where appropriate.

@@

Discuss the key aspects of your problem, data set and regression model(s). Given that you are working on real-world data, explain at a high-level your exploratory data analysis, how you prepared the data for regression modeling, your process for building regression models, and your model selection.

@@

Describe the specifics of what you did (data exploration, data preparation, model building, model selection, model evaluation, etc.), and what you found out (statistical analyses, interpretation and discussion of the results, etc.).

We used `r cite_r("Manuscript.bib")` for all our analyses.

@@

Conclude your findings, limitations, and suggest areas for future work.

>>>>

---
title             : "A Logistic Regression Qpproach to CoIL Challenge 2000"
shorttitle        : " "
author: 
  - name          : "Corey Arnouts"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "119 W 31st St., New York, NY 10001"
    email         : "Corey.Arnouts@spsmail.cuny.edu"
  - name          : "Adam Douglas"
    affiliation   : "1"
  - name          : "Jason Givens-Doyle"
    affiliation   : "1"
  - name          : "Michael Silva"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "MS in Data Science Students CUNY School of Professional Studies"
abstract: |
  A logistic regression based solution to the CoIL Challenge 2000 is described. The challenge consists of correctly identifying potential customers for an insurance product, and describing their characteristics.
  <!-- https://tinyurl.com/ybremelq 
    One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

@@

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  -->
keywords          : "CoIL Challenge, Logistic Regression"
wordcount         : "X"
bibliography      : ["Manuscript.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf:
    #citation_package: natbib #biblatex
  html_document: default
---

@@

# Introduction
<!-- Describe the background and motivation of your problem.-->

Businesses use data science to extract insights from data.  It has many practical business applications.  Identifying households to include in a marketing campaign is one application.  One example using real world data is the Computational Intelligence and Learning (CoIL) Challenge. The CoIL Challenge competition was held from March 17 to May 8 in 2000.  The challenge is to:

1.  Identify potential customers for an insurance policy; and

2.  Provide a description of this customer base.

In total 147 participants registered and 43 submitted solutions [@Putten]. In this paper we set out to complete the first part of the COIL Challenge. **SUMARISE FINDINGS?**

@@

<!--Discuss how other researchers have addressed similar problems, what their achievements are, and what the advantage and drawbacks of each reviewed approach are. Explain how your investigation is similar or different to the state-of-theart. Please cite the relevant papers where appropriate.-->

Participants used a variety of approaches in formulating their submissions including: Artificial Neural Networks [@Kim], Naïve Bayes [@Elkan].

The maximum number of policyowners that could be found was 238.  The winning model [@Elkan] selected 121 policy owners. Random selection results in 42 policy owners. The standard benchmark tests result in 94 (k-nearest neighbor), 102 (naïve bayes), 105 (neural networks) and 118 (linear!) policy owners. [@Putten]

<!--
Other solutions (in alphabetical order):

3 Achim Lewandowski. How to detect potential customers. [ps.gz], [pdf]

4 Alexander Seewald. CoIL Challenge 2000 Submitted Solution. [ps.gz], [pdf]

5 A.P. White and W.Z. Liu. The CoIL Challenge: an Application of Classification Trees with Bootstrap Aggregation. [ps.gz], [pdf]

6 Andrew Greenyer. Coil 2000 Competition. The use of a learning classifier system JXCS. [ps.gz], [pdf]

7 Arnold Koudijs. CoIL Challenge 2000 Submission for the Description Task. [ps.gz], [pdf]

8 William M. Crocoll. Artificial Neural Network Portion of Coil Study. [ps.gz], [pdf]

9 Chris Leckie and Herman Ferra. COIL Challenge 2000 Description Task. [ps.gz], [pdf]

10 Gustavo Denicolay and Gaston Morales. CoIL Challenge 2000 Submission for the Description Task. [ps.gz] [pdf]

11 Dragan Gamberger. Solution based on ILLM confirmation rule. [ps.gz], [pdf]

12 János Abonyi, Hans Roubos. A Simple Fuzzy Classifier based on Inconsistency Analysis of Labeled Data. [ps.gz],[pdf]

13 Jonathan Carter. Coil 2000 Challenge Submission: Genetic Algorithms and Hill-climbers. [ps.gz], [pdf]

14 Juha Vesanto and Janne Sinkkonen. Submission for the CoIL Challenge 2000. [ps.gz], [pdf]

15 Mark-André Krogel. A Data Mining Case Study. [ps.gz],[pdf]

16 Michel Bera and Bertrand Lamy. Kxen at CoIL Challenge 2000. [ps.gz], [pdf]

17 Paul Rickets. CoIL Challenge 2000 submission. [ps.gz], [pdf]

18 Petr Mikšovský, Jirí Klema. COIL Challenge 2000. [ps.gz], [pdf]

19 Petri Kontkanen. CoIL 2000 Submission. [ps.gz], [pdf]

20 Philip Brierley. COIL 2000 Challenge: Characteristics of caravan insurance policy owners. [ps.gz] [pdf]

21 Robert M. Simmonds. ACT Study report using Classification and Regression Tree (CART) Analysis. [ps.gz], [pdf]

22 S. Sathiya Keerthi and Chong Jin Ong. Solution of the CoIL Challenge 2000 Task Using Support Vector Machines. [ps.gz], [pdf]

23 Serhiy Shtovba, Yakiv Mashnitskiy. The Backpropagation Multilayer Feedforward Neural Network Based Competition Task Solution.

24 Serhiy Shtovba. Phase Intervals and Genetic Algorithms Based Competition Task Solution. [ps.gz], [pdf]

25 Jurgen A. Doornik and Steve Moyle. LOGIT Modelling. [ps.gz], [pdf]

26 Thomas Martini Jorgensen and Christian Linneberg. Subspace Projections – an approach to variable selection and modeling. [ps.gz], [pdf]

27 Tom McKone and Curt Stenger. COIL CHALLENGE 2000 Submission. [ps.gz], [pdf]

28 Tomislav Šmuc. COIL 2000 Challenge Solution based on ILLM-SG Methodology. [ps.gz], [pdf]

29 Uzay Kaymak and Magne Setnes. Target Selection based on fuzzy clustering: a volume prototype approach to CoIL Challenge 2000. [ps.gz], [pdf]

-->

@@

<!--Discuss the key aspects of your problem, data set and regression model(s). Given that you are working on real-world data, explain at a high-level your exploratory data analysis, how you prepared the data for regression modeling, your process for building regression models, and your model selection.

@@

<!--Describe the specifics of what you did (data exploration, data preparation, model building, model selection, model evaluation, etc.), and what you found out (statistical analyses, interpretation and discussion of the results, etc.).

We used `r cite_r("Manuscript.bib")` for all our analyses.
-->

@@

<!--Conclude your findings, limitations, and suggest areas for future work.-->

### 2019-11-08 final project/Manuscript.tex
Updated Final Project

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={CoIL Challenge Submission},
            pdfauthor={Corey Arnouts, Adam Douglas, Jason Givens-Doyle, \& Michael Silva},
            pdfkeywords={CoIL Challenge, Logistic Regression},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{CoIL Challenge Submission}
    \author{Corey Arnouts\textsuperscript{1}, Adam Douglas\textsuperscript{1}, Jason Givens-Doyle\textsuperscript{1}, \& Michael Silva\textsuperscript{1}}
    \date{}

\shorttitle{CoIL Challenge Submission}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} CUNY School of Professional Studies}
\keywords{CoIL Challenge, Logistic Regression\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\authornote{MS in Data Science Students

@@

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.

@@

Busineses use data science to extract insight from data. It has many practical business applications. The Computational Intelligence and Learning (CoIL) Challenge showcases the power data science can bring to bear on fundamental business problems.

The CoIL Challenge was a datamining competition held from March 17 to May 8 in 2000. Participants could:

\begin{itemize}
\tightlist
\item
  Predict which customers are potentially interested in a caravan insurance policy; and
\item
  Describe the actual or potential customers; and possibly explain why these customers buy a caravan policy.
\end{itemize}

In total 147 participants registered and 43 submitted solutions (Putten, Ruiter, \& Someren, 2000). The winners of the challenge were Charles Elkan for the prediction task and Nick Street and YongSeog Kim for the description task.

In this paper we set out to complete the prediction part of the COIL Challenge ourselves using a logistic regression classifier. \textbf{SUMARISE FINDINGS}

@@

Discuss how other researchers have addressed similar problems, what their achievements are, and what the advantage and drawbacks of each reviewed approach are. Explain how your investigation is similar or different to the state-of-theart. Please cite the relevant papers where appropriate.

@@

Discuss the key aspects of your problem, data set and regression model(s). Given that you are working on real-world data, explain at a high-level your exploratory data analysis, how you prepared the data for regression modeling, your process for building regression models, and your model selection.

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.

Describe the specifics of what you did (data exploration, data preparation, model building, model selection, model evaluation, etc.), and what you found out (statistical analyses, interpretation and discussion of the results, etc.).

We used R (Version 3.6.1; R Core Team, 2019) and the R-package \emph{\}papaja} {[}@\}R-papaja{]} for all our analyses.

Conclude your findings, limitations, and suggest areas for future work.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Putten-2000}{}%
Putten, P., Ruiter, M., \& Someren, M. (2000). CoIL challenge 2000 tasks and results: Predicting and explaining caravan policy ownership.

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

>>>>

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={A Logistic Regression Qpproach to CoIL Challenge 2000},
            pdfauthor={Corey Arnouts, Adam Douglas, Jason Givens-Doyle, \& Michael Silva},
            pdfkeywords={CoIL Challenge, Logistic Regression},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{A Logistic Regression Qpproach to CoIL Challenge 2000}
    \author{Corey Arnouts\textsuperscript{1}, Adam Douglas\textsuperscript{1}, Jason Givens-Doyle\textsuperscript{1}, \& Michael Silva\textsuperscript{1}}
    \date{}

\shorttitle{ }
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} MS in Data Science Students CUNY School of Professional Studies}
\keywords{CoIL Challenge, Logistic Regression\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\authornote{

@@

\abstract{
A logistic regression based solution to the CoIL Challenge 2000 is described. The challenge consists of correctly identifying potential customers for an insurance product, and describing their characteristics.

@@

Businesses use data science to extract insights from data. It has many practical business applications. Identifying households to include in a marketing campaign is one application. One example using real world data is the Computational Intelligence and Learning (CoIL) Challenge. The CoIL Challenge competition was held from March 17 to May 8 in 2000. The challenge is to:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Identify potential customers for an insurance policy; and
\item
  Provide a description of this customer base.
\end{enumerate}

In total 147 participants registered and 43 submitted solutions (Putten, Ruiter, \& Someren, 2000). In this paper we set out to complete the first part of the COIL Challenge. \textbf{SUMARISE FINDINGS?}

@@

Researchers used a variety of approaches in formulating their submissions including: Artificial Neural Networks (Kim \& Street, 2000), Naïve Bayes (Elkan, 2000).

@@

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Elkan}{}%
Elkan, C. (2000). CoIL challenge 2000 entry. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/ELKANP~1.pdf}

\leavevmode\hypertarget{ref-Kim}{}%
Kim, Y., \& Street, W. N. (2000). CoIL challenge 2000: Choosing and explaining likely caravan insurance customers. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/STREET~1.pdf}

\leavevmode\hypertarget{ref-Putten}{}%
Putten, P., Ruiter, M., \& Someren, M. (2000). CoIL challenge 2000 tasks and results: Predicting and explaining caravan policy ownership.
